High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2021-05-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars. We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors. However, very likely due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation. This is summarised in the second panel of Fig.~\ref{fig:polarring}, where it shows the centroids of the Gaussian fitting at each azimuth for both optimization. The curve that follows these fitted centroids for each of the optimizations goes almost entirely within the errors of the other one, leaving the window open to the discussion of if this differences are just a consequence of the pointing error or are they a real notable feature of the disc.

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (see the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from large dust grains rather than directly from the stars. The main blob of this dust structure is at estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au. If this feature is caused by the presence of millimetre-sized dust, assuming optically thin emission, i.e. following
\begin{multline}
    \label{optically_thin_equation}
      M_{blob} = 0.03 M_{\sun} \left(\frac{F}{1\,\mathrm{Jy}}\right) \left(\frac{d}{100\,\mathrm{pc}}\right)^2 \left(\frac{\lambda}{1.3\,\mathrm{mm}}\right)^3 
      \\
      \left(\frac{50\,\mathrm{K}}{T}\right)    \left(\frac{0.02\,\mathrm{cm^2/g}}{\kappa_{1.3\,\mathrm{mm}}}\right),
\end{multline}
where $F$ is the total flux of the blob, $d$ the distance of 71.4\,pc , $\lambda$ the wavelength, $\kappa_{1.3\,\mathrm{mm}}$ the opacity at 1.3\,mm and the temperature set at $T=500\,\mathrm{K}$. Then, its estimated mass would be around 0.12\,M$_{\earth}$.

@@

The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, available online in \textsc{vizier}. We also used archival \textit{Spitzer} IRS spectroscopic data available in the CASSIS database \citep{Lebouteiller_2015} (see Fig.~\ref{fig:SED}). The SED describe the characteristic “dip” near 10 $\micron$, a common element of transition disk, as described by \citet{Rosenfeld_2013}. \citet{Jensen_97} concluded that these data matched that of a extended circumbinary disk truncated at $\sim$0.3\,au, as the interior would also be expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}.

@@

The multi-frequency data can be interpreted in terms of a physical structure using radiative transfer predictions, for which we used the \textsc{radmc3d} package \citep[version 2.0,][]{Dullemond_2012}. The general framework of the parametric model that we developed is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}, \citet{Ru_z_Rodr_guez_2019} and \citet{2019ApJ...882..160Q}. Computing a high-resolution radiative transfer model that succeeds in the reproduction of multi-frequency imaging and the SED, is finding a solution to a very degenerative problem, so obtaining an ideal model with a full parameter exploration requires a level of computation and time that exceeds our capabilities. Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data. Then, we improved this fit implementing one dimensional chi squared optimizations for some key parameters (more on this in sec.~\ref{sec:results}). The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel surface density profiles for gas, large and small dust grains, and in the bottom panel the aspect ratio profile.

@@

Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging. We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach higher regions above the mid-plane.

@@

For the vertical structure, \citet{dOrazi} found flaring angles (i.e. height of the ring over the disk midplane divided by the radius of the ring), of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. Our model aims to reproduce those values by using two different flaring indices, $\psi_1$ and $\psi_2$. The separation between the two values was set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24. The scale height is set to $H_\circ = 0.94$\,au at $r_\circ = 18$\,au. This is summarized in bottom panel of Fig.~\ref{fig:profiles} that shows the aspect ratio profile $h(r)=H(r)/r$.

Although both ALMA and SPHERE--IRDIS images display two-ringed morphologies, we propose a three-ringed structure plus an inner disc to reproduce the observations. This bold decision is due the major fit improvement in the SED (more on this in sec.~\ref{sec:results}). We separate the disc into four individual regions: the inner disc, Ring5, Ring13, and Ring24. The combined gas surface density profile is then given by:
\begin{equation}
  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring5}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
\end{equation}

@@

For Ring24 we used the same power-law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}(r)$ and by $\epsilon(r)$, a parameter that allows us model a smoother inner edge of the outer ring:
\begin{equation}
  \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}}(r)\,\epsilon(r),
\end{equation}
with
\begin{equation}
  \delta_{\mathrm{sd}}(r) =
  \begin{cases}
  0    & r < 18\text{\,au} \\
  4.2\times 10^4 & r > 18\text{\,au},
  \end{cases}
\end{equation}
and 
\begin{equation}
    \epsilon(r) = 
    \begin{cases}
  0    & r < R_\mathrm{in} \,\, {\rm and} \,\, R_\mathrm{peak} < r \\
  \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3 & R_\mathrm{in} < r < R_\mathrm{peak},
    \end{cases}
\end{equation}
where $R_\mathrm{in}$ and $R_\mathrm{peak}$ respectively mark the inner edge and the location of maximum density of the outer ring. We used $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.4\,au.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a larger inner cavity, a larger gap between Ring13 and Ring24, and a break in the outer ring. We only included a low density of large grains within Ring5, just underneath the detection limit of the ALMA observation, as it does not show any visible signature.We also truncated the profile of large dust grains at 63\,au. It is then defined by the sum of its three components
\begin{equation}
  \Sigma_{\mathrm{ld}}(r) = \Sigma_{\mathrm{Ring5,ld}} + 
  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
\end{equation}

For Ring5 and Ring13, we chose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.2$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.1$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.4\,\mathrm{g\,cm^{-3}}$. For Ring24 we used a similar profile as for the gas (a power-law function). The surface density for large dust grains in the outer ring is thus given by
\begin{equation}
    \Sigma_{\mathrm{Ring24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{-\gamma_{\mathrm{ld}}} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{2-\gamma_{\mathrm{ld}}}\right]\,\delta_{\mathrm{ld}}(r) \,\epsilon(r),
\end{equation}
where
\begin{equation}
  \delta_{\mathrm{ld}}(r) =
  \begin{cases}
  0                 & r < 24.6\text{\,au} \\
  7.2 \times10^{4} & 24.6 < r < 27.9\text{\,au} \\
  3.2 \times10^{4} & 27.9 < r < 35.3\text{\,au} \\
  2.7 \times10^{5} & 35.3 < r < 64\text{\,au.} \\
  \end{cases}
\end{equation}
and for $\epsilon(r)$ we used $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$. In an effort to recreate the break seen in the outer ring, we used
\begin{equation}
  \gamma_{\mathrm{ld}}(r) =
  \begin{cases}
  3.5 & 27.9\text{\,au} < r < 35.3\text{\,au} \\
    1                 &  {\rm elsewhere} \\

  \end{cases}
\end{equation}

Then the final density of large dust can be calculated as
\begin{equation}
\rho_{\mathrm{large\,dust}}(r,z)=
\frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta .
\end{equation}

The two different populations of dust grains correspond to small grains, with radii ranging from 0.3 to 1.5\,$\micron$, and large dust grains, with radii from 0.3\,$\micron$ to 10\,mm. We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.

@@

@@

As mentioned before, the model presented here gives a solution to a very degenerative problem. Nevertheless, as a way to improve and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion. Varying the value for one parameter and calculating chi-square for each new value, given $\chi^2_m$ the model chi squared value, the uncertainties (up and down) will be those with $\chi^2=\chi^2_m+1$. Assuming a quadratic behavior for the curve fitting, we can estimate that the scale height at $r_\circ$= 18\,au is $H_\circ = 0.92^{+0.01}_{-0.01}$\,au, the width of Ring13 is $w_\mathrm{g} = 5.18^{+0.42}_{-0.16}$\,au for the gas and $w_\mathrm{g} = 2.00^{+0.08}_{-1.4}$\,au, the location of Ring5 is $r=5.2^{+0.05}_{-0.7}$\,au and its width is $w_\mathrm{Ring5} = 0.59^{+0.08}_{-0.36}$\,au.

\begin{figure*}
	\includegraphics[width=\textwidth]{plot_chi_all.pdf}
        \caption{one dimensional explorations of the chi squared space of our parametric model. {\it Top:} scale height at $r_\circ$=18\,au, width of }
    \label{fig:chi}
\end{figure*}

@@

The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24. The introduced Ring5 is not visible in the simulated image as its predicted peak intensity is around two times the noise in the ALMA image ($\sim$1$\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$). This gives us an upper limit for the total millimetre-sized dust mass present in Ring5 of $\sim$2$\times10^{-5}$\,M$_{\earth}$. The depletion of large dust grains in Ring5 is consistent with efficient dust trapping in Ring13. A zone of radially increasing gas pressure can entirely filter out large dust grains from inner regions, while smaller grains can be able to overcome this barrier due to their strong frictional coupling to the gas accretion flow \citep[studied in the context of planetary gaps,][]{Rice2006,Zhu2012,Weber2018}. Still, the strong depletion of large particles demands that within Ring5 dust evolution is very inefficient or limited, or that large particles are very rapidly removed. Otherwise, the present small grains should quickly coagulate to form detectable grain sizes in the ALMA observation in Fig.~\ref{fig:images_vs_simulated} \citep{Drazkowska2019}. The central emission is not present in the simulated 1.3 mm continuum image as it was impossible to achieve a bright blob without disrupting the SED fit (read below).

As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13. Accordingly, taking the parametric model values for Ring13, it has a radius of 13.22\,au, a FWHM of 2.00\,au, and a scale height FWHM of the millimetre-sized dust of 0.6\,au. The total dust mass of Ring13 is about 0.7\,M$_{\earth}$ in the model. In turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and break at $\sim$36\,au. It contains a total dust mass of $\sim$44\,M$_{\earth}$. The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation. Since the scale height FWHM of the large grains in Ring13 is 0.6\,au, and has a measured width of 2.46$\pm$0.40\,au (See sec.~\ref{subsec:ALMA}), the ring is 4.1$\pm$0.9 times more extended radially than vertically.

@@

The effective beam size of the presented ALMA observations marginally resolves the FWHM of Ring13 to be $w_\mathrm{d} = 2.46\pm0.40$\,au. Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 5.42^{+0.01}_{-1.15}$\,au, we can see that large dust grains have to be radially converged to explain the discrepancy.

@@

@@

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

>>>>

In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars. We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors. However, quite likely due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation. This is summarised in the second panel of Fig.~\ref{fig:polarring}, where it shows the centroids of the Gaussian fitting at each azimuth for both optimization. The curve that follows these fitted centroids for each of the optimizations goes almost entirely within the errors of the other one, leaving the window open to the discussion of if this differences are just a consequence of the pointing error or are they a real notable feature of the disc.

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (see the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from large dust grains rather than directly from the stars. The main blob of this dust structure is at estimated distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a mean FWHM of $\sim$1.43\,au. \citet{Francis_2020} also did some measurements of this central emission by assuming a power--law profile for an inner disk that goes from 0.1 to 4\,au, and has a total dust mass of 0.013$\pm$0.002\,M$_{\earth}$. They stated that the inner radius of the disk is well beyond the sublimation radius as the system shows a low--NIR excess but a clear millimetre emission.

%If this feature is caused by the presence of millimetre-sized dust, assuming optically thin emission, i.e. following
%\begin{multline}
%    \label{optically_thin_equation}
%      M_{blob} = 0.03 M_{\sun} \left(\frac{F}{1\,\mathrm{Jy}}\right) \left(\frac{d}{100\,\mathrm{pc}}\right)^2 \left(\frac{\lambda}{1.3\,\mathrm{mm}}\right)^3 
%      \\
 %     \left(\frac{50\,\mathrm{K}}{T}\right)    %\left(\frac{0.02\,\mathrm{cm^2/g}}{\kappa_{1.3\,\mathrm{mm}}}\right),
%\end{multline}
%where $F$ is the total flux of the blob, $d$ the distance of 71.4\,pc , $\lambda$ the wavelength, $\kappa_{1.3\,\mathrm{mm}}$ the opacity at 1.3\,mm and the temperature set at $T=500\,\mathrm{K}$. Then, its estimated mass would be around 0.12\,M$_{\earth}$.

@@

The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, available online in \textsc{vizier}. We also used archival \textit{Spitzer} IRS spectroscopic data available in the CASSIS database \citep{Lebouteiller_2015} (see Fig.~\ref{fig:SED}). The SED describe the characteristic “dip” near 10 $\micron$, a common element of transition disc, as described by \citet{Rosenfeld_2013}. \citet{Jensen_97} concluded that these data matched that of a extended circumbinary disc truncated at $\sim$0.3\,au, as the interior would also be expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}.

@@

The multi-frequency data can be interpreted in terms of a physical structure using radiative transfer predictions, for which we used the \textsc{radmc3d} package \citep[version 2.0,][]{Dullemond_2012}. The general framework of the parametric model that we developed is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}, \citet{Ru_z_Rodr_guez_2019} and \citet{2019ApJ...882..160Q}. Computing a high-resolution radiative transfer model that succeeds in the reproduction of multi-frequency imaging and the SED, is finding a solution to a highly degenerative problem, so obtaining an ideal model with a full parameter exploration requires a level of computation and time that exceeds our capabilities and the scope of this paper. Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data, and then, improve this fit by implementing one dimensional chi squared optimizations for some key parameters (more on this in sec.~\ref{sec:results}). The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel surface density profiles for gas, large and small dust grains, and in the bottom panel the respective aspect ratio profile.

@@

Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging. We built the model in terms of the gas distribution, and with two main dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach higher regions above the mid-plane. And we also added a third dust population of large grains and with a tightly confined distribution and a special size range just to account for the central emission.

@@

For the vertical structure, \citet{dOrazi} found flaring angles (i.e. height of the ring over the disc midplane divided by the radius of the ring), of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. Our model aims to reproduce those values by using two different flaring indices, $\psi_1$ and $\psi_2$. The separation between the two values was set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24. The scale height is set to $H_\circ = 0.94$\,au at $r_\circ = 18$\,au. This vertical structure is consistent with the measurements made by \citet{dOrazi}, as the model flaring angles are $\varphi_{\mathrm{inner}}$ = 6.5\,$\degr$ and $\varphi_{\mathrm{outer}}$ = 7.9\,$\degr$. This is summarized in bottom panel of Fig.~\ref{fig:profiles} that shows the aspect ratio profile $h(r)=H(r)/r$.

Although both ALMA and SPHERE--IRDIS images display two-ringed morphologies, we propose a three-ringed structure plus an inner disc to reproduce the observations. This bold decision is due the major fit improvement in the SED and the polarize image (more on this in sec.~\ref{sec:results}). We separate the disc into four individual regions: the inner disc, Ring5, Ring13, and Ring24. The combined gas surface density profile is then given by:
\begin{equation}
  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring5}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
\end{equation}

@@

For Ring24 we used the same power-law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}(r)$ and by $\epsilon(r)$, a parameter that allows us model a smoother inner edge of the outer ring:
\begin{equation}
  \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}}(r)\,\epsilon(r),
\end{equation}
with $\delta_{\mathrm{sd}}(r) = 4.2\times 10^4$ for $r > 18$\,au and zero for lower radii, and
%\begin{equation}
%  \delta_{\mathrm{sd}}(r) =
%  \begin{cases}
%  0    & r < 18\text{\,au} \\
%  4.2\times 10^4 & r > 18\text{\,au},
%  \end{cases}
%\end{equation}
\begin{equation}
    \epsilon(r) = 
    \begin{cases}
  1    & r < R_\mathrm{in} \,\, {\rm and} \,\, R_\mathrm{peak} < r \\
  \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3 & R_\mathrm{in} < r < R_\mathrm{peak},
    \end{cases}
\end{equation}
where $R_\mathrm{in}$ and $R_\mathrm{peak}$ respectively mark the inner edge and the location of maximum density of the outer ring. We used $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.4\,au.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a larger inner cavity, a larger gap between Ring13 and Ring24, and a break in the outer ring. We only included a low density of large grains within Ring5, just underneath the detection limit of the ALMA observation, as it does not show any visible signature. We also truncated the profile of large dust grains at 63\,au. It is then defined by the sum of its three components
\begin{equation}
  \Sigma_{\mathrm{ld}}(r) = \Sigma_{\mathrm{Ring5,ld}} + 
  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
\end{equation}

For Ring5 and Ring13, we chose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.2$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.1$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.4\,\mathrm{g\,cm^{-3}}$. For Ring24 we used a similar profile as for the gas (a power-law function). The surface density for large dust grains in the outer ring is thus given by
\begin{equation}
    \Sigma_{\mathrm{Ring24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{-\gamma_{\mathrm{ld}}} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{2-\gamma_{\mathrm{ld}}}\right]\,\delta_{\mathrm{ld}}(r) \,\epsilon(r),
\end{equation}
where
\begin{equation}
  \delta_{\mathrm{ld}}(r) =
  \begin{cases}
  0                 & r < 24.6\text{\,au} \\
  7.2 \times10^{4} & 24.6 < r < 27.9\text{\,au} \\
  3.2 \times10^{4} & 27.9 < r < 35.3\text{\,au} \\
  2.7 \times10^{5} & 35.3 < r < 64\text{\,au.} \\
  \end{cases}
\end{equation}
and for the smoothing factor $\epsilon(r)$ we used $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$. In an effort to recreate the break seen in the outer ring, we used
\begin{equation}
  \gamma_{\mathrm{ld}}(r) =
  \begin{cases}
  3.5 & 27.9\text{\,au} < r < 35.3\text{\,au} \\
    1                 &  {\rm elsewhere} \\
  \end{cases}
\end{equation}

Then the final density of large dust can be calculated as
\begin{equation}
\rho_{\mathrm{large\,dust}}(r,z)=
\frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta.
\end{equation}

These two different populations of dust grains correspond to small grains, with radii ranging from 0.3 to 1.5\,$\micron$, and large dust grains, with radii from 0.3\,$\micron$ to 10\,mm. We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.

@@

For the reproduction of central emission we introduce a special dust population that is distributed only on a very close Gaussian ring parameterized by $\mu_{\mathrm{central\,blob}}=1.1$\,au, $\sigma_{\mathrm{central\,blob}}=0.4$\,au and $\Sigma_{\circ,\mathrm{central\,blob}}=2.4\,\mathrm{g\,cm^{-3}}$, and following the argument of \citet{Francis_2020}, it goes in past the sublimation radius until it reaches the grid boundary. This dust population has grains with radii ranging from 0.8 to 10\,mm, same upper limit as the large dust but is depleted of small grains. This different size range is a way to avoid creating excess NIR in the SED and to be consistent with previous mass estimates (see Appendix~\ref{sec:Appendix}). As the ring is extremely proximate to the binary system the dust will not have any traces of ice, so we used a composition mix of 70\% silicate and 30\% graphite.

@@

As mentioned before, the model presented here gives a solution to a highly degenerative problem. Nevertheless, as a way to improve and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix.~\ref{sec:Appendix}). We can estimate that the scale height at $r_\circ$= 18\,au is $H_\circ = 0.92^{+0.01}_{-0.01}$\,au, the width of Ring13 is $w_\mathrm{g} = 5.18^{+0.42}_{-0.16}$\,au for the gas and $w_\mathrm{g} = 2.00^{+0.08}_{-1.4}$\,au, the location of Ring5 is $r=5.2^{+0.05}_{-0.7}$\,au and its width is $w_\mathrm{Ring5} = 0.59^{+0.08}_{-0.36}$\,au.

@@

The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24. The introduced Ring5 is not visible in the simulated image as its predicted peak intensity is around two times the noise in the ALMA image ($\sim$1$\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$). This gives us an upper limit for the total millimetre-sized dust mass present in Ring5 of $\sim$2$\times10^{-5}$\,M$_{\earth}$. The depletion of large dust grains in Ring5 is consistent with efficient dust trapping in Ring13. A zone of radially increasing gas pressure can entirely filter out large dust grains from inner regions, while smaller grains can be able to overcome this barrier due to their strong frictional coupling to the gas accretion flow \citep[studied in the context of planetary gaps,][]{Rice2006,Zhu2012,Weber2018}. Still, the strong depletion of large particles demands that within Ring5 dust evolution is extremely inefficient or limited, or that large particles are rapidly removed. Otherwise, the present small grains should quickly coagulate to form detectable grain sizes in the ALMA observation in Fig.~\ref{fig:images_vs_simulated} \citep{Drazkowska2019}. The central emission is not present in the simulated 1.3 mm continuum image as it was impossible to achieve a bright blob without disrupting the SED fit (read below).

As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13. Accordingly, taking the parametric model values for Ring13, it has a radius of 13.22\,au, a FWHM of 2.00\,au, and a scale height FWHM of the millimetre-sized dust of 0.6\,au. The total dust mass of Ring13 is about 0.7\,M$_{\earth}$ in the model. In turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and break at $\sim$36\,au. It contains a total dust mass of $\sim$45\,M$_{\earth}$, that stands under the lower limit of 60\,M$_{\earth}$ inferred by \citet{Ru_z_Rodr_guez_2019} from a previous 860\,$\micron$ continuum ALMA image. The model predictions for the millimetre-sized dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation. Since the scale height FWHM of the large grains in Ring13 is 0.6\,au, and has a measured width of 2.46$\pm$0.40\,au (See sec.~\ref{subsec:ALMA}), the ring is 4.1$\pm$0.9 times more extended radially than vertically. The central emission radial profile is also well reproduced, and the lack of a high NIR excess indicate that the dust in this blob must be at least bigger than 0.5\,mm (see Appendix~\ref{sec:Appendix}). In addition, our interpretation of a Gaussian close ring agrees with the mass estimates of \citet{Francis_2020} with a dust mass of 0.012\,M$_{\earth}$, implying a slightly higher lower limit for the dust population around the central region.

@@

The effective beam size of the presented ALMA observations marginally resolves the FWHM of Ring13 to be $w_\mathrm{d} = 2.46\pm0.40$\,au. Using that the FWHM of the gas in Ring13 in the RT model corresponds to $w_\mathrm{g} = 5.42^{+0.01}_{-1.15}$\,au, we can see that large dust grains have to be radially converged to explain the discrepancy.

@@

  \item The central emission observed by ALMA might be by

@@

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
\appendix

\section{Parameter--space exploitation} \label{sec:Appendix}

The model presented here has many degrees of freedom and each model requires a high level of computational power and time, so a MCMC optimization or similar methods of parameter exploration are impossible to acquire. But as a way to compute a measure of goodness of fit and to try to quantify the improvements we did a partial exploration of the parameter space. Varying the value for one parameter and calculating chi-square for each new value, given $\chi^2_m$ the model chi squared value, the uncertainties (up and down) will be those with $\chi^2=\chi^2_m+1$. Assuming a quadratic behavior for the curve fitting,
\begin{figure*}
	\includegraphics[width=\textwidth]{plot_chi_all.pdf}
        \caption{one dimensional explorations of the chi squared space of our parametric model. {\it Top:} scale height at $r_\circ$=18\,au, width of }
    \label{fig:chi}
\end{figure*}

The
